### 2013-09-17 manuscripts/reply/reply.tex
More work on reply.
Beginning work on EB section.

\section*{EB}
\citet{Hickerson2013} repeatedly refer the prior distributions used by
\citet{Oaks2012} as ``poorly selected''.

>>>>

\section*{EB}
\citet{Hickerson2013} repeatedly refer the prior distributions used by
\citet{Oaks2012} as ``poorly selected''.
However, this is bit misleading, as \citet{Oaks2012} discuss in detail how the
selected their priors (see their section ``Specifying and simulating the joint
prior'').
They detail how the being limited to uniform prior distributions necessitates
awkward broad priors to avoid excluding the truth, a priori.
What \citet{Hickerson2013} really mean to say is that \citet{Oaks2012} did not
use an empirical Bayesian approach, which is what they do and advocate.

Given all of this, it is quite clear why one should use caution before
overly criticizing ones choice of priors after having seen the posterior.
This really is a strawman argument.
They were not there before the data were seen.
